%
% Daftar Pustaka 
% 

% 
% Tambahkan pustaka yang digunakan setelah perintah berikut. 
% 
\begin{thebibliography}{4}

\bibitem{r.patric}
{Patric. \f{Accelerate R Applications with CUDA}. 2014. \url{https://devblogs.nvidia.com/parallelforall/accelerate-r-applications-cuda/}.}

\bibitem{r.venables}
{W. N. Venables dan D. M. Smith. \f{Introduction to R}. 2016.}

\bibitem{r.beckmw}
{Beckmw. \f{A brief foray into parallel processing with R}. 2014. }

\bibitem{r.leach}
{Clint Leach. \f{Introduction to Parallel Computing in R}. 2014. }

\bibitem{r.schmidt}
{Drew Schmidt. \f{High Performance Computing with R}. 27 Februari 2015. }

\bibitem{r.schwendinger}
{Florian Schwendinger, Gregor Kastner, Stefan Theußl. \f{High Performance Computing with Applications in R}. 28 September 2015. }

\bibitem{opencl.howto}
{Askubuntu.com. \f{How to make OpenCL work on 14.10 + Nvidia 331.89 drivers?}. 10 Oktober 2014. \url{http://askubuntu.com/questions/541114/how-to-make-opencl-work-on-14-10-nvidia-331-89-drivers}.}

\bibitem{opencl.mmul}
{Zaius. \f{Matrix Multiplication 1 (OpenCL)}. 22 September 2009. \url{http://gpgpu-computing4.blogspot.co.id/2009/09/matrix-multiplication-1.html}.}

\bibitem{opencl.mukherjee}
{Mukherjee, S et al. \f{Exploring the Features of OpenCL 2.0}. 2015. IWOCL }

\bibitem{opencl.ebook}
{Banger, R, Bhattacharyya .K. \f{OpenCL Programming by Example}. 2013. Packt publishing }

\bibitem{opencl.clgetplatforminfo}
{Stackoverflow. \f{What is the right way to call clGetPlatformInfo?}. 21 Juni 2013. \url{http://stackoverflow.com/questions/17240071/what-is-the-right-way-to-call-clgetplatforminfo}.}

\bibitem{blas.netlib}
{Netlib.org. \f{About BLAS}. 15 November 2015. \url{http://www.netlib.org/blas/​​}.}

\bibitem{blas.wiki}
{Wikipedia. \f{Basic Linear Algebra Subprograms}. 10 Mei 2016. \url{https://en.wikipedia.org/wiki/Basic_Linear_Algebra_Subprograms}.}

\bibitem{opencl.clblas}
{ClMath. \f{ClBLAS}. 2016. \url{https://github.com/clMathLibraries/clBLAS}.}

\bibitem{opencl.clblas.tutorial}
{Nugteren, C. \f{ClBLAS Tutorial}. 2014. \url{http://www.cedricnugteren.nl/tutorial.php?page=1}.}

\bibitem{opencl.mygemm}
{Nugteren, C. \f{MyGEMM}. 2014. \url{https://github.com/cnugteren/myGEMM}.}

\bibitem{opencl.cuda.porting}
{sharcnet.ca. \f{Porting CUDA to OpenCL}. 2014. \url{https://www.sharcnet.ca/help/index.php/Porting_CUDA_to_OpenCL}.}

\bibitem{opencl.gaussianblur}
{Karapetsas, L. \f{Playing with OpenCL: Gaussian Blurring}. 2014. \url{ http://blog.refu.co/?p=663 }.}

​
\end{thebibliography}
